---
title: "Balanced Arrays"
output:
  pdf_document: default
---

## Balanced Array

Given an array of numbers, find the index of the smallest array element (the pivot), for which the sums of all elements to the left and to the right are equal. The array may not be reordered.

Example

arr=[1,2,3,4,6]

the sum of the first three elements, 1+2+3=6. The value of the last element is 6. 
Using zero based indexing, arr[3]=4 is the pivot between the two sub-arrays.
The index of the pivot is 3.
 
Function Description 

Complete the function balancedSum in the editor below.

balancedSum has the following parameter(s):

    int arr[n]:  an array of integers

Returns:

    int: an integer representing the index of the pivot

Constraints

3 * n * 105
1 * arr[i] * 2 * 104, where 0 * i < n
It is guaranteed that a solution always exists.

```{r}

balancedSum <- function(len, nums) {
  lp <- 1; rp <- len
  lsum <- 0; rsum <- 0
  
  while(lp < rp) {
    if(lsum <= rsum) {
      lsum <- sum(lsum, nums[lp])
      lp <- lp + 1
    } else {
      rsum = sum(rsum, nums[rp])
      rp <- rp - 1
    }
    
    if(lsum == rsum)
      break
  }
  
  stopifnot(lp == rp)
  
  return(lp)
}

```

## Base Case

```{r}
arr <- c(4,1,2,3)

balancedSum(arr)
```

### Test Cases

```{r}

problem_name <- "balanced-array"
problem_path <- here::here(problem_name, "test_cases")

test_cases <- list()

for(file in list.files(problem_path)) {
  
  test_file <- file.path(problem_path, file)
  test_data <- readLines(test_file)
  n <- test_data[1]; arr <- as.numeric(test_data[2:length(test_data)])
  
  test_cases <- c(list(test_case = file,
                       result = balancedSum(n, arr)))
}

test_data <- readLines(test_file)
```

